Binning Strategies and Related Loss for Large Data

### 2015-04-24 Paper.Rnw
baseball - frequencies label top left

<<BaseballBinnedScatters2X10,echo=F,include=T,eval=T,fig.width=12, fig.height=4, out.width='.99\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, warning=F, fig.show='hold',fig.cap="Binned Scatterplots for Games vs Strikeouts">>=  
 # raw frequencies plot
p1 <- qplot(binxs, binys, geom="tile", fill=binfreq, data=binout1[[1]],
      main="Standard Freq Binning") +
  xlab("Games (count)") + ylab("Strike Outs (count)")+
  scale_fill_gradient("Frequencies", low="#56B1F7", high="#132B43") + 
  theme_bw() + theme(legend.position="bottom",aspect.ratio=1,
                     legend.key.width = unit(1, "cm"),
                     panel.grid= element_blank(),
                     plot.margin = unit(c(0.5,-.5,.1,-.5),"cm"),
                     legend.text=element_text(size=12) )
# # bin frequencies distribution hugely skewed
# qplot(binfreq, geom="density", data= binout1[[1]], color=I("blue")) + theme_bw()
# qplot(log(binfreq), geom="density", data= binout1[[1]], color=I("blue")) + theme_bw()

>>>>

<<BaseballBinnedScatters2X10,echo=F,include=T,eval=T,fig.width=12, fig.height=4, out.width='.99\\linewidth', fig.pos='h',fig.align='center',tidy=F, cache=TRUE, warning=F, fig.show='hold',fig.cap="Binned Scatterplots for Games vs Strikeouts">>=  
 # raw frequencies plot
p1 <- qplot(binxs, binys, geom="tile", fill=binfreq, data=binout1[[1]],
      main="Standard Freq Binning") +
  xlab("Games (count)") + ylab("Strike Outs (count)")+
  scale_fill_gradient("Frequencies", low="#56B1F7", high="#132B43",
                      guide=guide_colourbar( 
                                        legend.key.width = unit(1, "cm"),
                                             legend.text=element_text(size=12),
                                            label.hjust=0.5,  
                                         title.position = "top")) + 
  theme_bw() + theme(aspect.ratio=1, 
                     panel.grid= element_blank(),
                     plot.margin = unit(c(0.5,-.5,.1,-.5),"cm"),
                     legend.position="bottom")
# # bin frequencies distribution hugely skewed
# qplot(binfreq, geom="density", data= binout1[[1]], color=I("blue")) + theme_bw()
# qplot(log(binfreq), geom="density", data= binout1[[1]], color=I("blue")) + theme_bw()
